Introducing statistics with \\texttt{intRo}

### 2014-12-05 student-paper-competition-2014/paper.Rmd
Table instead of graphic for education section

The features of \texttt{intRo} were selected in order to apply to the most commonly used lesson plans in early statistics courses. The textbook "The Art and Science of Learning from Data" by Agresti and Franklin [-@agresti2012statistics] references many of the focal points of introductory statistics, and \texttt{intRo} supports performing a majority of them. Part one, titled "Gathering and Exploring Data", covers graphical summaries, measures of spread and center, and avoiding the misuse of graphics in situations they are not appropriate. \texttt{intRo} includes modules for both graphical and numerical summaries covering these topics. Furthermore, \texttt{intRo} limits the display of variables to ones that are appropriate for a chosen plot type, helping to reinforce the appropriateness of particular graphics (Figure \ref{fig:ag}).

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{images/appropriate_graphics.png}
\caption{The plot and variable selection boxes in \texttt{intRo}'s graphical module. Because the selected plottype is histogram, the interface displays only a single variable selection box (x), and the variables selectable in this box are only numeric.}
\label{fig:ag}
\end{figure}

Part two of this text discusses probability and sampling distributions, which is outside the current realm of \texttt{intRo}, but part three focuses on inferential statistics. The inferential statistics include confidence intervals, hypothesis testing, and comparing two variables, all supported natively in \texttt{intRo}. Finally, part four of the text discusses the association between variables, including regression, functions that \texttt{intRo} performs with ease. Some of the more advanced topics of this section are currently unsupported by \texttt{intRo}, including multiple regression and nonparametric statistics.

>>>>

The features of \texttt{intRo} were selected in order to apply to the most commonly used lesson plans in early statistics courses. The textbook "The Art and Science of Learning from Data" by Agresti and Franklin [-@agresti2012statistics] references many of the focal points of introductory statistics, and \texttt{intRo} supports performing a majority of them. Part one, titled "Gathering and Exploring Data", covers graphical summaries, measures of spread and center, and avoiding the misuse of graphics in situations they are not appropriate. \texttt{intRo} includes modules for both graphical and numerical summaries covering these topics. Furthermore, \texttt{intRo} limits the display of variables to ones that are appropriate for a chosen plot type, helping to reinforce the appropriateness of particular graphics (Table \ref{tab:plottypes}).

\begin{table}[ht!]
\centering
\begin{tabular}{|c|c|c|}
\hline
Plot Type&X Variable Type Allowed&Y Variable Type Allowed\\
\hline
Histogram&Numeric&N/A\\
Normal Quantile Plot&Numeric&N/A\\
Scatterplot&Numeric&Numeric\\
Line Chart&Numeric&Numeric\\
Boxplot&Categorical&Numeric\\
Bar Chart&Categorical&Numeric\\
Pareto Chart&Categorical&Numeric\\
Mosaic Plot&Categorical&Categorical\\
\hline
\end{tabular}
\label{tab:plottypes}
\caption{The plot and variable types allowed in \texttt{intRo}'s graphical module. For example, when the selected plottype is histogram, the interface displays only a single variable selection box (x), and the variables selectable in this box are only numeric. If a boxplot is selected, the x variable must be categorical and the y variable must be numeric, and the list of choices updates automatically to reflect this.}
\end{table}
Part two of this text discusses probability and sampling distributions, which is outside the current realm of \texttt{intRo}, but part three focuses on inferential statistics. The inferential statistics include confidence intervals, hypothesis testing, and comparing two variables, all supported natively in \texttt{intRo}. Finally, part four of the text discusses the association between variables, including regression, functions that \texttt{intRo} performs with ease. Some of the more advanced topics of this section are currently unsupported by \texttt{intRo}, including multiple regression and nonparametric statistics.
